Scikit-learn: API design for machine learning

### 2013-06-17 paper.tex
move parallel processing from implementation to future work
Also trimmed it quite a bit. Left out the memory overhead argument
because it isn't entirely fair; this is a by-product of parallel
processing in general, as well as our implementation. It is aggravated
by the environment, not caused by it.

Finally, some estimators in \sklearn also support multi-core architectures.
Machine learning algorithms can indeed often be decomposed into independent
smaller tasks that may each be solved in parallel, thereby reducing the overall
computing times. At this point in time, support for multi-core programming in
Python -- at least in the CPython implementation targeted by scikit-learn -- is
however suboptimal. The interpreter supports multithreading, but due to the
\textit{global interpreter lock}, no two threads in a process may execute Python
code at the same time. It follows that multithreading is not a viable solution
for parallelizing parts of an algorithm, even for embarrassingly parallel
problems, such as fitting and evaluating multiple models in a grid search
procedure. The workaround that we use is to rely on the Python multiprocessing
module, which emulates threads using multiple operating system- level processes.
However this solution is not perfect as it may in turn lead to a large memory
overhead since objects (e.g., input datasets) need to be copied within each
process own memory space. In some cases, it may unfortunately even happen that
the overhead becomes so significant that fully exploiting a multi-core
architecture becomes infeasible due memory constraints. As such, a proper
implementation of parallel machine learning algorithms remain a challenging task
for the project.

@@

\section{Conclusions and future works}
\label{sec:conclusions}

@@

At a lower-level, a potential point of improvement is parallel processing,
which, as described in Section~\ref{sec:implementation}, is only implemented at a
rather coarse-grained level. Cython built-in support for OpenMP
\citep{dagum1998openmp} remains a viable candidate technology for more fine-
grained multicore support in \sklearn.

>>>>

@@

\section{Conclusions and future work}
\label{sec:conclusions}

@@

At a lower-level, parallel processing is a potential point of improvement.
Some estimators in \sklearn are already able to leverage multi-core processors,
but only in a coarse-grained fashion.
At present, parallel processing is difficult to accomplish in the Python environment;
\sklearn targets the main implementation, CPython,
which cannot execute Python code on multiple CPUs simultaneously.
It follows that any parallel task decomposition must either be done
inside Cython modules,
or at a level high enough to warrant the overhead
of creating multiple OS-level processes,
and the ensuing inter-process communication.
Parallel grid search is an example of the latter approach
which has already been implemented.
Recent versions of Cython include support for the OpenMP standard
\citep{dagum1998openmp},
which is a viable candidate technology
for more fine-grained multicore support in \sklearn.
